PARTIAL TRACKING VIA LINEAR PROGRAMMING

### 2017-04-17 paper/paper.tex
Adding a cleaned up matrix prep routine
Doesn't yet work. I believe it is because the inequality constraints need to be separated or else there are too few
and the program is unbounded. What needs to happen: for example for each node, you cannot count the number of
incoming nodes in total, you must count them using separate constraints. In the end the number of non-zero values
in the constraint matrix is the same, but there are more constraints.
Removed redundant equations and unnecessary variables
Have finished describing the algorithm in the paper. Need to finish writing
complexity analysis.

\documentclass{article}
\usepackage{waspaa17,amsmath,graphicx,url,times}
%\usepackage{waspaa17,amssymb,amsmath,graphicx,times,url}
\usepackage{color}
\usepackage[ruled]{algorithm2e}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[labelsep=period]{caption}

@@

@@

Typically the DTSTFT is computed for a block of contiguous samples, called a
\textit{frame} and these frames are computed every $H$ samples, $H$ being the
\textit{hop-size}. We will denote the $M$ sets of parameters at local maxima in
frame $h$ as $\theta_0^{h}, \dotsc, \theta_{M-1}^{h}$ and the $N$ in frame $h+1$
as $\theta_0^{h+1}, \dotsc, \theta_{N-1}^{h+1}$ where $h$ and $h+1$ refer to
adjacent frames. We are interested in paths that extend across $K$ frames where
each path touches only one parameter set and each parameter set is either
exclusive to a single path or is not on a path.

@@

In \cite[p.~748]{mcaulay1986speech} the peak matching algorithm is described in
a number of steps; we summarize them here in a way comparable with the linear
programming formulation to be presented shortly. In that paper, the parameters
of adjacent frames $h$ and $h+1$ are the instantaneous amplitude, phase, and
frequency and are indexed by frequency as $\omega_0^{h}, \dotsc,
\omega_{M-1}^{h}$ and $\omega_0^{h+1}, \dotsc, \omega_{N-1}^{h+1}$ but we will
allow for arbitrary parameter sets.  Define a distance function $\mathcal{D}
\left( \theta_{i},\theta_{j} \right)$ that computes the
similarity between $2$ sets of parameters. We will now consider a method that
finds $L$ tuples of parameters that are closest.

We compute the cost tensor %$\boldsymbol{C}$
$
    \boldsymbol{C} = \theta^{h}
    \otimes_{\mathcal{D}} \mathellipsis \otimes_{\mathcal{D}} \theta^{h+K-1}
$.
For each $l \in \left[0 \dotsc L-1 \right]$, find the indices
$i_{0},\dotsc,i_{K-1}$ 
corresponding to the shortest
distance, then remove the $i_{0},\dotsc,i_{K-1}$th rows (lines of table entries)
in the their respective dimensions from consideration
and continue until $L$ tuples have been determined or the distances exceed some
threshold $\Delta$. This is summarized in Algorithms~\ref{alg:mq_peak_match}

\begin{algorithm}
    \KwIn{the cost matrix $\boldsymbol{C}$}
    \KwOut{$L$ tuples of indices $\Gamma$, or fewer if $\Delta$ exceeded}
    $\Gamma \leftarrow \varnothing$\;
    \For{$l \leftarrow 0$ to $L-1$}{
        $\D \Gamma_{l}=\argmin_{[0,\dotsc,M_{0}-1] \times
        \mathellipsis \times [0,\dotsc,M_{K-1}-1] \setminus \Gamma}
            \boldsymbol{C}$\;
            \If{$ C_{\Gamma_{l}} > \Delta$}{
            \KwRet{$\Gamma$}
        }
        $\Gamma \leftarrow \Gamma \cup C_{\Gamma_{l}}$\;
    }
    \KwRet{$\Gamma$}
    \caption{A generalized McAulay-Quatieri peak-matching algorithm.}%
    \label{alg:mq_peak_match}
\end{algorithm}

@@

\section{An optimal method \label{sec:lppathsearch}}

There is a way to find a set of paths over multiple frames ($K > 2$) having the
lowest total cost if
we restrict the search to exactly $L$ paths. Instead of indexing parameters by
their frame number $h$, we make $h$ part of the parameter set so that it can be
used by the distance function $\mathcal{D}$. Assume that over $K$ frames there
are $M$ total parameter sets. In this context we will consider them as nodes in
a graph. We define the vector $\boldsymbol{c} \in \mathbb{R}^{M^2}$
where the entry $\boldsymbol{c}_{i + Mj} = \mathcal{D} \left( \theta_{i}, \theta_{j}
\right)$. If we have a set of connections $\Gamma_{i,j}$ we can calculate the
total cost of these connections by defining the vector
\[
    \boldsymbol{x}_{i + Mj} = \begin{cases}
        1 & \text{there is a connection between }i\text{ and }j\\
        0 & \text{otherwise}
    \end{cases}
\]
and then forming the inner product
\[
    c_{\text{total}}=\left\langle \boldsymbol{c},\boldsymbol{x} \right\rangle
\]
Note that a node cannot be connected to itself. The question is how to find
$\boldsymbol{x}^{\ast}$ so that $c_{\text{total}}$ is minimized. How do we
constrain $\boldsymbol{x}$ to give us a solution to the partial tracking
problem? Let us consider an example.

In Figure~\ref{plot:simple_graph} we have an example of a simple graph or
lattice. Such a graph represents a plausible partial tracking situation:
vertically aligned nodes are parameter sets estimated from the same analysis
frame and we would like to connect these parameter sets between frames. The
numbers are indices of nodes in the graph and the edges (possible connections) between
them are indicated by lines. Imagine that we would like to
find the two shortest paths. We will now examine the resulting paths from two
algorithms using different criteria for shortness.

In Figure~\ref{plot:simple_graph_greedy_paths} we find the paths using an
algorithm similar to Algorithms~\ref{alg:mq_peak_match} but search instead over a
tensor of distances $C \in \mathbb{R}^{3 \times 4 \times 2}$ whose entry
$C_{i,j,h}$ represents the cost of travelling on the path connecting the $i$th
node in layer 0, the $j$th node in layer 1 and the $h$th node in layer 2. This
cost is the sum of the Euclidean distances giving the lengths of the
connections. This is the greedy method of searching for the best paths whose
optimality criterion is to find the set of best paths containing the absolute
best path. We see in Figure~\ref{plot:simple_graph_greedy_paths} that the
absolute shortest path, $1 \rightarrow 4 \rightarrow 8$, is discovered, followed
by the second shortest path not using the nodes of the first path, $2
\rightarrow 5 \rightarrow 7$.

\begin{figure}[!t]
    \centering
    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex.eps}}
    \CaptionWithTitle{%
        \input{plots/small_graph_ex.txt}%
    }{\label{plot:simple_graph}}
\end{figure}

\begin{figure}[!t]
    \centering
    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex_greedy_paths.eps}}
    \CaptionWithTitle{%
        \input{plots/small_graph_ex_greedy_paths.txt}%
    }{\label{plot:simple_graph_greedy_paths}}
\end{figure}

\subsection{$L$ shortest paths via linear programming}

To find a set of paths minimizing the total cost, we instead search for total
solutions $\boldsymbol{x}$ that describe all paths in the graph. Assume for now
that we can guarantee that the entries of $\boldsymbol{x}$ will be either 0 or
1. To find a set of constraints for our search, we consider the structure of a
valid solution $\boldsymbol{x}^{\ast}$. To maintain that paths not overlap, a
valid solution's nodes are only allowed to have one edge entering ---
coming from a node in a previous frame --- and one edge leaving
--- going to a node in a successive frame. To translate this into a
constraint, consider the node $i$ and its possible $R_{i}$ successive connecting
nodes $j_{0} \dotsc j_{R_{i}-1}$. Define the vector\footnote{The superscript s
stands for ``successive''.}
\[
    a^{\text{s},i}_{i + Mj_{r}} = \begin{cases}
        1 & \forall j_{r} \in \left[ j_{0} \dotsc j_{R_{i}-1} \right] \\
        0 & \text{otherwise}
    \end{cases}
\]
As all the entries of $\boldsymbol{x}$ are either 0 or 1, we have
\[
    0 \leq \left\langle \boldsymbol{a}^{\text{s},i}, \boldsymbol{x} \right\rangle \leq 1
\]
so we can make this a constraint to ensure that a node has at most one path
leaving. Similarly, if we consider the node $j$ and its possible $R_{j}$ previous connecting
nodes $i_{0} \dotsc i_{R_{j}-1}$, the vector\footnote{The superscript p
stands for ``previous''.}
\[
    a^{\text{p},j}_{i_{r} + Mj} \begin{cases}
        1 & \forall i_{r} \in \left[ i_{0} \dotsc i_{R_{j}-1} \right] \\
        0 & \text{otherwise}
    \end{cases}
\]
constrains that node $j$ have only one path entering through the constraint
\[
    0 \leq \left\langle \boldsymbol{a}^{\text{p},j} , \boldsymbol{x} \right\rangle \leq 1
\]
A node on a path will also have an edge entering and an edge leaving. To
translate this into a constraint, we define a vector that counts the number of
edges entering a node and subtracts then the number of edges leaving a node. The
result should always be 0 for an equal number of edges entering and exiting a
node. If $r$ is the index of the node considered, the vector is simply
\footnote{The superscript b stands for ``balanced''.}
\[
    \boldsymbol{a}^{\text{b},r} = \boldsymbol{a}^{\text{p},r} -
    \boldsymbol{a}^{\text{s},r}
\]
and the constraint
\[
    \left\langle \boldsymbol{a}^{\text{b},r}, \boldsymbol{x} \right\rangle = 0
\]
Finally we want to constrain that there be only $L$ paths. We do this by
noticing that if this is true, there will be $L$ edges between frames $h$ and
$h+1$. We constrain the number of paths going from edges
$\Gamma_{h}$ in frame $h$ to $\Gamma_{h+1}$ by forming the vector
\footnote{The superscript c stands for ``connections''.}
\[
    \boldsymbol{a}^{\text{c},h} = \sum_{j \in \Gamma_{h}}
    \boldsymbol{a}^{\text{s},j}
\]
and asserting the constraint
\[
    \left\langle \boldsymbol{a}^{\text{c},h} , \boldsymbol{x} \right\rangle = L
\]
The length of $\boldsymbol{x}$ is $M^{2}$ so the total size of all the
constraints is not insignificant, but most entries in the constraint vectors will
be 0 and therefore the resulting constraint matrices very sparse, so sparse
linear algebra routines can be used in computations. Furthermore, the
$\boldsymbol{a}^{b}$ and $\boldsymbol{a}^{c}$ constraints are derived from
$\boldsymbol{a}^{p}$ and $\boldsymbol{a}^{s}$, so only the latter need to be
stored.

\begin{figure}[!t]
    \centering
    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex_lp_paths.eps}}
    \CaptionWithTitle{%
        \input{plots/small_graph_ex_lp_paths.txt}%
    }{\label{plot:simple_graph_lp_paths}}
\end{figure}

The complete \textit{linear program (LP)} solving the $L$ shortest paths problem is then
\[
    \min_{\boldsymbol{x}} \left\langle \boldsymbol{c}, \boldsymbol{x} \right\rangle
\]
subject to
\[
    \boldsymbol{0} \leq
    \begin{bmatrix}
        \boldsymbol{A}_{\text{s}} \\
        \boldsymbol{A}_{\text{p}}
    \end{bmatrix} \boldsymbol{x}
    \leq \boldsymbol{1}
\]
\[
    \begin{bmatrix}
        \boldsymbol{A}_{\text{b}} \\
        \boldsymbol{A}_{\text{c}}
    \end{bmatrix}
    \boldsymbol{x}
    =
    \begin{bmatrix}
        \boldsymbol{0} \\
        L\boldsymbol{1}
    \end{bmatrix}
\]
\[
    \boldsymbol{0} \leq \boldsymbol{x} \leq \boldsymbol{1}
\]
where $\boldsymbol{A}_{\text{s}}$ is the matrix with
$\boldsymbol{a}^{\text{s},m}$ as its rows for $m \in [0 \dotsc M-1]$ and
$\boldsymbol{A}_{\text{p}}$ is the matrix with $\boldsymbol{a}^{\text{p},m}$ as
its rows, etc.

The solution of the two best paths using the LP formulation
is shown in Figure~\ref{plot:simple_graph_lp_paths} and a comparison of the
total costs is shown in Table~\ref{tab:greedy_lp_cost_compare}

\begin{table}[!b]
    \caption{\label{tab:greedy_lp_cost_compare} Comparison of total costs in
    Figure~\ref{plot:simple_graph_lp_paths}}
    \begin{center}
        \begin{tabular}{c c}
            Greedy & LP \\
            \hline
            \input{plots/small_graph_ex_greedy_cost.txt} &
            \input{plots/small_graph_ex_lp_cost.txt} \\
        \end{tabular}
    \end{center}
\end{table}

The LP formulation is inspired by a multiple object tracking algorithm for video
\cite{jiang2007linear}. A proof that the solution $\boldsymbol{x}^{\ast}$ will
have entries equal to either $0$ or $1$ can be found in
\cite[p.~167]{parker1988discrete}. The theoretical computational complexity of
the linear program is polynomial in the number of variables, see
\cite{karmarkar1984new} for a proof and the demonstration of a fast algorithm
for finding its solution. In practice, to extract paths from the solution, we do
not test equality with $0$ or $1$ but rather test if the solution vector's
values are greater than some threshold.

@@

We compare the greedy and LP based methods for peak matching on a synthetic
signal. The signal is composed of $K=6$ chirps of constant amplitude, the $k$th
chirp $s$ at sample $n$ described by the equation
\[
    s_{k}(n) = \exp(j(\phi_{k} + \omega_{k}n +
    \frac{1}{2} \psi_{k} n^{2}))
\]
The parameters for the 6 chirps are presented in
Table~\ref{tab:ptrackexamplechirpparams}.

>>>>

\documentclass{article}
\usepackage{waspaa17,amsmath,graphicx,url,times}
%\usepackage{waspaa17,amssymb,amsmath,graphicx,times,url}
\usepackage{color}
\usepackage[ruled]{algorithm2e}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[labelsep=period]{caption}
%\usepackage{mathabx}

@@

% symbol definitions
\newcommand{\cLP}{\boldsymbol{c}_{\rho}}
\newcommand{\BS}[1]{\boldsymbol{#1}}

@@

Typically the DTSTFT is computed for a block of contiguous samples, called a
\textit{frame} and these frames are computed every $H$ samples, $H$ being the
\textit{hop-size}. We will denote the $N_{k}$ sets of parameters at local maxima in
frame $k$ as $\theta_0^{k}, \dotsc, \theta_{N_{k}-1}^{k}$ and the $N_{k+1}$ in frame $k+1$
as $\theta_0^{k+1}, \dotsc, \theta_{N_{k+1}-1}^{k+1}$ where $k$ and $k+1$ refer to
adjacent frames. We are interested in paths that extend across $K$ frames where
each path touches only one parameter set and each parameter set is either
exclusive to a single path or is not on a path.

\subsection{Note on notation}

In this paper, indexing starts at 0. If we have a vector $\BS{x}$ then
$\BS{x}_{i}$ is the $i$th row or column of that vector depending on the
orientation. The same notation is used for cartesian products, e.g., if $\alpha$
and $\beta$ are sets and $A =
\alpha \times \beta$ then for the pair $a \in A$ $a_{0}$ is the first item in
the pair and $a_{1}$ the second.

The number of frames is denoted $K$, the number of nodes in the $k$th frame $N_k$ and
the total number of nodes $M = \sum_{k=0}^{K-1} N_{k}$. $\theta_{i}^{j}$ is the
$i$th node of the $j$th frame, $\theta^{j}$ the set of all the nodes in the
$j$th frame and $\theta_{m}$ the $m$th node out of all $M$ nodes ($0 \leq m <
M$).

@@

In \cite[q.~748]{mcaulay1986speech} the peak matching algorithm is described in
a number of steps; we summarize them here in a way comparable with the linear
programming formulation to be presented shortly. In that paper, the parameters
of each data point are the instantaneous amplitude, phase, and frequency but we
will allow for arbitrary parameter sets $\theta$.  Define a distance function
$\mathcal{D}
\left( \theta_{i},\theta_{j} \right)$ that computes the
similarity between $2$ sets of parameters. We will now consider a method that
finds $L$ tuples of parameters that are closest.

We compute the cost tensor
$
    \BS{C} = \theta^{k}
    \otimes_{\mathcal{D}} \mathellipsis \otimes_{\mathcal{D}} \theta^{k+K-1}
$.
For each $l \in \left[0 \dotsc L-1 \right]$, find the indices
$i_{0},\dotsc,i_{K-1}$ 
corresponding to the shortest
distance, then remove the $i_{0},\dotsc,i_{K-1}$th rows (lines of table entries)
in the their respective dimensions from consideration
and continue until $L$ tuples have been determined or the distances exceed some
threshold $\Delta_{\text{MQ}}$. This is summarized in Algorithms~\ref{alg:mq_peak_match}

\begin{algorithm}
    \KwIn{the cost matrix $\BS{C}$}
    \KwOut{$L$ tuples of indices $\Gamma$, or fewer if $\Delta_{\text{MQ}}$ exceeded}
    $\Gamma \leftarrow \varnothing$\;
    \For{$l \leftarrow 0$ to $L-1$}{
        $\D \Gamma_{l}=\argmin_{[0,\dotsc,M_{0}-1] \times
        \mathellipsis \times [0,\dotsc,M_{K-1}-1] \setminus \Gamma}
            \BS{C}$\;
            \If{$ C_{\Gamma_{l}} > \Delta_{\text{MQ}}$}{
            \KwRet{$\Gamma$}
        }
        $\Gamma \leftarrow \Gamma \cup C_{\Gamma_{l}}$\;
    }
    \KwRet{$\Gamma$}
    \caption{A generalized McAulay-Quatieri peak-matching algorithm.}%
    \label{alg:mq_peak_match}
\end{algorithm}

@@

\section{$L$ best paths through a lattice via linear programming (LP)}

In this section we show how to find L paths through a lattice of $K$ frames such
that the sets of nodes on each path are disjoint. The $k$th frame of the lattice
contains $N_{k}$ nodes for a total of $M = \sum_{k=0}^{K-1}N_{k}$ nodes.

Whereas the limiting cost underwhich a path would be considered was the sum of
the costs of all connections in the McAulay-Quatieri method, for the LP method
we define the cost $\Delta_{\text{LP}}$ as the limiting cost underwhich the
connection between two nodes will be considered.

The solution vector $\BS{x}$ to the linear program shall indicate the presence of a
connection between a pair of nodes by having an entry equal to $1$ and otherwise
have entries equal to $0$. To enumerate the set of possible connection-pairs we
define
\begin{equation}
    \rho = \left\{ (i,j) : \mathcal{D}(\theta_{i},\theta_{j}) \leq
    \Delta_{\text{LP}} , 0 \leq i < M, 0 \leq j < M, i \neq j \right\}
\end{equation}
The cost vector of the objective function is then 
\begin{equation}
    \cLP = \left\{ D(\theta_{i},\theta_{j}) \forall (i,j) \in
    \rho \right\}
\end{equation}
and the length of $\cLP$ is $\# \rho = \# \cLP = P$, in other words, $P$
pairs of nodes. For convenience we define a bijective mapping ${\mathcal{B} :
\rho \rightarrow [0, \mathellipsis, M-1]}$ giving the index in $\BS{x}$ of the
pair $p \in \rho$. For the implementation considered in this paper,
$\mathcal{D}(\theta_{i},\theta_{j}) = \infty$ for all $i,j$ not in adjacent
frames and so $P$ will be no larger than $(K-1)N^{2}$ (assuming the same
number of nodes $N$ in each frame).

The total cost of the paths in the solution is then calculated through the
inner product $\cLP^{T}\BS{x}$. To obtain $\BS{x}^{\ast}$ that represents $L$
disjoint paths we must place constraints on the structure of the solution. Some
of the constraints presented in the following are redundant but the redundancies
are kept for clarity; later we will show which constraints can be removed
without changing the optimal solution $\BS{x}^{\ast}$.

All nodes in $\BS{x}^{\ast}$ will have at most one incoming connection or
otherwise no connections, a constraint that can be enforced through the
following linear inequality. Define $\BS{A}^{\text{I}} \in
\mathbb{R}^{R_{\text{I}} \times P}$ with $R_{\text{I}} = \sum_{k=1}^{K-1}
N_{k}$, the number of nodes in all the frames excluding the first. We sum all
the connections into the node $r_{\text{I}} + N_{0}$ represented by the
respective entry in $\BS{x}$ through an inner product with the $r_{\text{I}}$th
row in $\BS{A}^{\text{I}}$ and require that this sum be between $0$ and $1$,
i.e.,
\begin{equation}
    \BS{A}^{\text{I}}_{r_{\text{I}},\mathcal{B}(p)} = \begin{cases}
        1 & \text{if } p_{1} = r_{\text{I}}+N_{0} \\
        0 & \text{otherwise}
    \end{cases}, 0 \leq r_{\text{I}} < R_{\text{I}}, p \in \rho
\end{equation}
and
\begin{equation}
    \BS{0} \leq \BS{A}^{\text{I}}\BS{x} \leq \BS{1}
\end{equation}
Similarly, to constrain the number of outgoing connections into each node, we
define $R_{\text{O}} = \sum_{k=0}^{K-2} N_{k}$ and
$\BS{A}^{\text{O}} \in \mathbb{R}^{R_{\text{O}} \times P}$ with
\begin{equation}
    \BS{A}^{\text{O}}_{r_{\text{O}},\mathcal{B}(p)} = \begin{cases}
        1 & \text{if } p_{0} = r_{\text{O}} \\
        0 & \text{otherwise}
    \end{cases}, 0 \leq r_{\text{O}} < R_{\text{O}}, p \in \rho
\end{equation}
and
\begin{equation}
    \BS{0} \leq \BS{A}^{\text{O}}\BS{x} \leq \BS{1}
\end{equation}

To ensure no breaks in the paths it is required that the number of incoming
connections into a given node equal the number of outgoing connections for the
$R_{\text{B}} = \sum_{k=1}^{K-2} N_{k}$ nodes potentially having both incoming
and outgoing connections.
\begin{equation}
    \BS{A}^{\text{B}}_{r_{\text{B}}} = \BS{A}^{\text{B}}_{r_{\text{B}}} -
    \BS{A}^{\text{B}}_{r_{\text{B}}+N_{0}} \text{ for rows } 0 \leq r_{\text{B}}
    < R_{\text{B}}
\end{equation}
and
\begin{equation}
    \label{eq:cxnbalcon}
    \BS{A}^{\text{B}}\BS{x} = \BS{0}
\end{equation}

Finally we ensure that there are $L$ paths by counting the number of connections
in each frame and constraining this sum to be $L$. We choose arbitrarily to
count the number of outgoing connections by summing rows of $\BS{A}^{\text{O}}$
into rows of $\BS{A}^{\text{C}} \in \mathbb{R}^{(K-1) \times P}$
\begin{equation}
    \BS{A}^{\text{C}}_{r_{\text{C}}} = \sum_{k=a}^{b} \BS{A}^{\text{O}}_{k}
\end{equation}
with $a = \sum_{j=0}^{r_{\text{C}}} N_{j}$ and $b = \sum_{j=0}^{r_{\text{C}}+1}
N_{j}$ and
\begin{equation}
    \label{eq:cxnlcon}
    \BS{A}^{\text{C}}\BS{x} = L\BS{1}
\end{equation}

As stated above, some of these constraints are redundant and can be removed.
Indeed, we have $\BS{0} \leq \BS{x} \leq \BS{1}$, therefore we will always have
$\BS{A}^{\text{I}}\BS{x} \geq 0$ and $\BS{A}^{\text{I}}\BS{x} \geq 0$.
Furthermore, all but the last row of (\ref{eq:cxnlcon}) can be seen as
constructed from linear combinations of rows of (\ref{eq:cxnbalcon}) and the last
row of (\ref{eq:cxnlcon}) so we only require $\BS{A}^{\text{C}}_{K-2}\BS{x} = L$.
Finally we always have $\BS{x} \leq \BS{1}$ because of the constraint that there
be a maximum of $1$ incoming and outgoing connection from each node.

The complete LP to find the $L$ best disjoint paths through a lattice described
by node connections $\rho$ is
\[
    \min_{\BS{x}} \cLP^{T} \BS{x} 
\]
subject to
\[
    \BS{G}\BS{x} =
    \begin{bmatrix}
        \BS{A}^{\text{I}} \\
        \BS{A}^{\text{O}} \\
        -\BS{I}
    \end{bmatrix} \BS{x} \leq
    \begin{bmatrix}
        \BS{1} \\
        \BS{1} \\
        \BS{0}
    \end{bmatrix}
\]
\begin{equation}
    \BS{A}\BS{x} =
    \begin{bmatrix}
        \BS{A}^{\text{B}} \\
        \BS{A}^{\text{C}}_{K-2}
    \end{bmatrix} \BS{x} = 
    \begin{bmatrix}
        \BS{0} \\
        L
    \end{bmatrix}
\end{equation}

% TODO: move to complexity

%\section{An optimal method \label{sec:lppathsearch}}
%
%There is a way to find a set of paths over multiple frames ($K > 2$) having the
%lowest total cost if
%we restrict the search to exactly $L$ paths. Instead of indexing parameters by
%their frame number $k$, we make $k$ part of the parameter set so that it can be
%used by the distance function $\mathcal{D}$. Assume that over $K$ frames there
%are $M$ total parameter sets. In this context we will consider them as nodes in
%a graph. We define the vector $\BS{c} \in \mathbb{R}^{M^2}$
%where the entry $\BS{c}_{i + Mj} = \mathcal{D} \left( \theta_{i}, \theta_{j}
%\right)$. If we have a set of connections $\Gamma_{i,j}$ we can calculate the
%total cost of these connections by defining the vector
%\[
%    \BS{x}_{i + Mj} = \begin{cases}
%        1 & \text{there is a connection between }i\text{ and }j\\
%        0 & \text{otherwise}
%    \end{cases}
%\]
%and then forming the inner product
%\[
%    c_{\text{total}}=\left\langle \BS{c},\BS{x} \right\rangle
%\]
%Note that a node cannot be connected to itself. The question is how to find
%$\BS{x}^{\ast}$ so that $c_{\text{total}}$ is minimized. How do we
%constrain $\BS{x}$ to give us a solution to the partial tracking
%problem? Let us consider an example.
%
%In Figure~\ref{plot:simple_graph} we have an example of a simple graph or
%lattice. Such a graph represents a plausible partial tracking situation:
%vertically aligned nodes are parameter sets estimated from the same analysis
%frame and we would like to connect these parameter sets between frames. The
%numbers are indices of nodes in the graph and the edges (possible connections) between
%them are indicated by lines. Imagine that we would like to
%find the two shortest paths. We will now examine the resulting paths from two
%algorithms using different criteria for shortness.
%
%In Figure~\ref{plot:simple_graph_greedy_paths} we find the paths using an
%algorithm similar to Algorithms~\ref{alg:mq_peak_match} but search instead over a
%tensor of distances $C \in \mathbb{R}^{3 \times 4 \times 2}$ whose entry
%$C_{i,j,k}$ represents the cost of travelling on the path connecting the $i$th
%node in layer 0, the $j$th node in layer 1 and the $k$th node in layer 2. This
%cost is the sum of the Euclidean distances giving the lengths of the
%connections. This is the greedy method of searching for the best paths whose
%optimality criterion is to find the set of best paths containing the absolute
%best path. We see in Figure~\ref{plot:simple_graph_greedy_paths} that the
%absolute shortest path, $1 \rightarrow 4 \rightarrow 8$, is discovered, followed
%by the second shortest path not using the nodes of the first path, $2
%\rightarrow 5 \rightarrow 7$.
%
%\begin{figure}[!t]
%    \centering
%    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex.eps}}
%    \CaptionWithTitle{%
%        \input{plots/small_graph_ex.txt}%
%    }{\label{plot:simple_graph}}
%\end{figure}
%
%\begin{figure}[!t]
%    \centering
%    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex_greedy_paths.eps}}
%    \CaptionWithTitle{%
%        \input{plots/small_graph_ex_greedy_paths.txt}%
%    }{\label{plot:simple_graph_greedy_paths}}
%\end{figure}
%
%\subsection{$L$ shortest paths via linear programming}
%
%To find a set of paths minimizing the total cost, we instead search for total
%solutions $\BS{x}$ that describe all paths in the graph. Assume for now
%that we can guarantee that the entries of $\BS{x}$ will be either 0 or
%1. In order to simplify the indexing in this section, we denote the number of
%nodes in each frame as $N_{k}$ ($M = \sum_{l=0}^{K-1} N_{k}$). To find a set of constraints for our search, we consider the structure of a
%valid solution $\BS{x}^{\ast}$. To maintain that paths not overlap, a
%valid solution's interior nodes (those not in the first or last frame) are only allowed to have one edge entering ---
%coming from a node in a previous frame --- and one edge leaving
%--- going to a node in a successive frame. To translate this into a
%constraint, consider the node $i$ and its possible $R_{i}$ successive connecting
%nodes $j_{0} \dotsc j_{R_{i}-1}$. Define the vector\footnote{The superscript s
%stands for ``successive''.}
%\[
%    a^{\text{s},i}_{i + Mj_{r}} = \begin{cases}
%        1 & \forall j_{r} \in \left[ j_{0} \dotsc j_{R_{i}-1} \right] \\
%        0 & \text{otherwise}
%    \end{cases}
%\]
%As all the entries of $\BS{x}$ are either 0 or 1, we have
%\[
%    0 \leq \left\langle \BS{a}^{\text{s},i}, \BS{x} \right\rangle \leq 1
%\]
%so we can make this a constraint to ensure that a node has at most one path
%leaving. Similarly, if we consider the node $j$ and its possible $R_{j}$ previous connecting
%nodes $i_{0} \dotsc i_{R_{j}-1}$, the vector\footnote{The superscript q
%stands for ``previous''.}
%\[
%    a^{\text{q},j}_{i_{r} + Mj} \begin{cases}
%        1 & \forall i_{r} \in \left[ i_{0} \dotsc i_{R_{j}-1} \right] \\
%        0 & \text{otherwise}
%    \end{cases}
%\]
%constrains that node $j$ have only one path entering through the constraint
%\[
%    0 \leq \left\langle \BS{a}^{\text{q},j} , \BS{x} \right\rangle \leq 1
%\]
%A node on a path will also have an edge entering and an edge leaving. To
%translate this into a constraint, we define a vector that counts the number of
%edges entering a node and subtracts then the number of edges leaving a node. The
%result should always be 0 for an equal number of edges entering and exiting a
%node. If $r$ is the index of the node considered, the vector is simply
%\footnote{The superscript b stands for ``balanced''.}
%\[
%    \BS{a}^{\text{b},r} = \BS{a}^{\text{q},r} -
%    \BS{a}^{\text{s},r}
%\]
%and the constraint
%\[
%    \left\langle \BS{a}^{\text{b},r}, \BS{x} \right\rangle = 0
%\]
%Finally we want to constrain that there be only $L$ paths. We do this by
%noticing that if this is true, there will be $L$ edges between frames $k$ and
%$k+1$. We constrain the number of paths going from edges
%$\Gamma_{k}$ in frame $k$ to $\Gamma_{k+1}$ by forming the vector
%\footnote{The superscript c stands for ``connections''.}
%\[
%    \BS{a}^{\text{c},k} = \sum_{j \in \Gamma_{k}}
%    \BS{a}^{\text{s},j}
%\]
%and asserting the constraint
%\[
%    \left\langle \BS{a}^{\text{c},k} , \BS{x} \right\rangle = L
%\]
%The length of $\BS{x}$ is $M^{2}$ so the total size of all the
%constraints is not insignificant, but most entries in the constraint vectors will
%be 0 and therefore the resulting constraint matrices very sparse, so sparse
%linear algebra routines can be used in computations. Furthermore, the
%$\BS{a}^{\text{b}}$ and $\BS{a}^{\text{c}}$ constraints are derived from
%$\BS{a}^{\text{q}}$ and $\BS{a}^{\text{s}}$, so only the latter need to be
%stored.
%
%\begin{figure}[!t]
%    \centering
%    \centerline{\includegraphics[width=\figwidthscale\textwidth]{plots/small_graph_ex_lp_paths.eps}}
%    \CaptionWithTitle{%
%        \input{plots/small_graph_ex_lp_paths.txt}%
%    }{\label{plot:simple_graph_lp_paths}}
%\end{figure}
%
%The complete \textit{linear program (LP)} solving the $L$ shortest paths problem is then
%\[
%    \min_{\BS{x}} \left\langle \BS{c}, \BS{x} \right\rangle
%\]
%subject to
%\[
%    \BS{0} \leq
%    \begin{bmatrix}
%        \BS{A}_{\text{s}} \\
%        \BS{A}_{\text{q}}
%    \end{bmatrix} \BS{x}
%    \leq \BS{1}
%\]
%\[
%    \begin{bmatrix}
%        \BS{A}_{\text{b}} \\
%        \BS{A}_{\text{c}}
%    \end{bmatrix}
%    \BS{x}
%    =
%    \begin{bmatrix}
%        \BS{0} \\
%        L\BS{1}
%    \end{bmatrix}
%\]
%\[
%    \BS{0} \leq \BS{x} \leq \BS{1}
%\]
%where $\BS{A}_{\text{s}}$ is the matrix with
%$\BS{a}^{\text{s},m}$ as its rows for $m \in [0 \dotsc M-1]$ and
%$\BS{A}_{\text{q}}$ is the matrix with $\BS{a}^{\text{q},m}$ as
%its rows, etc.
%
%The solution of the two best paths using the LP formulation
%is shown in Figure~\ref{plot:simple_graph_lp_paths} and a comparison of the
%total costs is shown in Table~\ref{tab:greedy_lp_cost_compare}
%
%\begin{table}[!b]
%    \caption{\label{tab:greedy_lp_cost_compare} Comparison of total costs in
%    Figure~\ref{plot:simple_graph_lp_paths}}
%    \begin{center}
%        \begin{tabular}{c c}
%            Greedy & LP \\
%            \hline
%            \input{plots/small_graph_ex_greedy_cost.txt} &
%            \input{plots/small_graph_ex_lp_cost.txt} \\
%        \end{tabular}
%    \end{center}
%\end{table}
%
%The LP formulation is inspired by a multiple object tracking algorithm for video
%\cite{jiang2007linear}. A proof that the solution $\BS{x}^{\ast}$ will
%have entries equal to either $0$ or $1$ can be found in
%\cite[q.~167]{parker1988discrete}. The theoretical computational complexity of
%the linear program is polynomial in the number of variables, see
%\cite{karmarkar1984new} for a proof and the demonstration of a fast algorithm
%for finding its solution. In practice, to extract paths from the solution, we do
%not test equality with $0$ or $1$ but rather test if the solution vector's
%values are greater than some threshold. 
%

@@

We compare the greedy and LP based methods for peak matching on a synthetic
signal. The signal is composed of $Q=6$ chirps of constant amplitude, the $q$th
chirp $s$ at sample $n$ described by the equation
\[
    s_{q}(n) = \exp(j(\phi_{q} + \omega_{q}n +
    \frac{1}{2} \psi_{q} n^{2}))
\]
The parameters for the 6 chirps are presented in
Table~\ref{tab:ptrackexamplechirpparams}.

\begin{table}[!b]
    \caption{Parameters of $q$th chirp. $\nu_{0}$ and $\nu_{1}$ are the initial and
    final frequency of the chirp in Hz. \label{tab:ptrackexamplechirpparams}}
    \begin{center}
        \begin{tabular}{l c c c c c}
            $q$ & $\phi_{q}$ & $\omega_{q}$ & $\psi_{q}$ & $\nu_{0}$ & $\nu_{1}$ \\
            \hline
            \input{plots/mq_lp_compare_chirp_params.txt}
        \end{tabular}
    \end{center}
\end{table}
